Using Visual Analytics to Explain\\[1ex] Black-Box Machine Learning

### 2018-04-06 aggexplain/experiment.tex
single typo

\subsection{Tasks and Measurements}
In order to test conditions against each other we created a questionnaire.
After asking the participant about the knowledge of machine learning and basic terminology, we have a training section for participants to familiarize themselves with the interface.
First, an introductory video explains all components of the interface.
The video uses an example model from a different data set which is designed to predict whether a room is occupied or not based on predictions from various sensors~\cite{occupancy}.
Then, a series of questions about this example model are asked and the participant can and has to use the interface to answer them correctly.
The questions ask about the values of features under certain conditions, such as ``What is the model's prediction for high values of `$CO_2$?''', ``What is the lowest value of `Humidity' that predicts `occupied'?'', ``Are the predictions for low values of `Light' correct?''.
The questions are constructed in a way to be easily answerable under all conditions given an understanding of the user interface and basic principles of machine learning.
An incorrect answer leads back to the beginning of the section and the participant is given the chance to correct the mistake.
We did not use those questions to exclude any participant but rather for giving them an opportunity to get comfortable with the user interface.
Note, that it is not necessary for participants to have a deep knowledge in \emph{how} machine learning algorithms work, as long as, the basic principles of prediction, ground truth, or accuracy are clear.  This reflects that domain experts would often not necessarily be trained in \emph{developing} machine learning models but rather \emph{using} them.

>>>>

\subsection{Tasks and Measurements}
In order to test conditions against each other we created a questionnaire.
After asking the participant about the knowledge of machine learning and basic terminology, we have a training section for participants to familiarize themselves with the interface.
First, an introductory video explains all components of the interface.
The video uses an example model from a different data set which is designed to predict whether a room is occupied or not based on predictions from various sensors~\cite{occupancy}.
Then, a series of questions about this example model are asked and the participant can and has to use the interface to answer them correctly.
The questions ask about the values of features under certain conditions, such as ``What is the model's prediction for high values of `$CO_2$'?'', ``What is the lowest value of `Humidity' that predicts `occupied'?'', ``Are the predictions for low values of `Light' correct?''.
The questions are constructed in a way to be easily answerable under all conditions given an understanding of the user interface and basic principles of machine learning.
An incorrect answer leads back to the beginning of the section and the participant is given the chance to correct the mistake.
We did not use those questions to exclude any participant but rather for giving them an opportunity to get comfortable with the user interface.
Note, that it is not necessary for participants to have a deep knowledge in \emph{how} machine learning algorithms work, as long as, the basic principles of prediction, ground truth, or accuracy are clear.  This reflects that domain experts would often not necessarily be trained in \emph{developing} machine learning models but rather \emph{using} them.
